My title

### 2024-12-01 paper/paper.qmd
Added in heatmap graph and updated facet wrap direction for some graphs

@@

number_of_cases_city |>
  ggplot(mapping = aes(x = arrest_was_not_made, y = proportion_of_cases)) +
  # Creates two graphs based on the status of the case
  facet_wrap(facets = vars(city), dir = "v") +
  geom_bar(stat = "identity", fill = "#936639") +
  theme_minimal() +
  labs(x = "Status of the homicide case", y = "Proportion of cases") +
  theme(legend.position = "bottom")
```
```{r}
#| label: tbl-city-table
#| tbl-cap: "Proportion and number of solved and unsolved homicides in Los Angeles and New York (2010 to 2017)"
#| echo: false
#| warning: false
#| message: false

@@

number_of_cases_victim_sex |>
  ggplot(mapping = aes(x = victim_sex, y = proportion_of_cases)) +
  # Creates two graphs based on the status of the case
  facet_wrap(facets = vars(arrest_was_not_made), dir = "v") +
  geom_bar(stat = "identity", fill = "#a4ac86") +
  theme_minimal() +
  labs(x = "Victim's Sex", y = "Proportion of cases") +
  theme(legend.position = "bottom")
```

@@

number_of_cases_victim_race |>
  ggplot(mapping = aes(x = victim_race, y = num_of_cases_victim_race)) +
  # Creates two graphs based on the status of the case
  facet_wrap(facets = vars(arrest_was_not_made), dir = "v") +
  geom_bar(stat = "identity", fill = "#a4ac86") +
  theme_minimal() +
  labs(x = "Victim's Race", y = "Number of cases") +
  theme(legend.position = "bottom")
```

>>>>

```{r}
#| label: fig-year-month-heatmap
#| fig-cap: "Number of solved and unsolved homicides from January to December from 2010 to 2017 in Los Angeles and New York"
#| echo: false
#| warning: false
#| message: false

number_of_cases_year_month <- 
  analysis_data_homicides |>
  # Group by solved and unsolved homicides and year
  group_by(arrest_was_not_made, year) |>
  # Count number of solved and unsolved homicides for each month per year 
  count(month)|>
  # Rename count column
  rename(
    "num_of_cases_month_year" = n
  ) |>
  mutate(
    month = case_when(
      (month == 1) ~ "Jan",
      (month == 2) ~ "Feb",
      (month == 3) ~ "Mar",
      (month == 4) ~ "Apr",
      (month == 5) ~ "May",
      (month == 6) ~ "Jun",
      (month == 7) ~ "Jul",
      (month == 8) ~ "Aug",
      (month == 9) ~ "Sep",
      (month == 10) ~ "Oct",
      (month == 11) ~ "Nov",
      (month == 12) ~ "Dec",
      TRUE ~ "None")
  ) |>
  mutate(
    arrest_was_not_made = case_when(
      (arrest_was_not_made == 1) ~ "Arrest was not made",
      (arrest_was_not_made == 0) ~ "Arrest was made",
      TRUE ~ "None")
  )

# To sort month in certain order 
# Referenced: https://www.geeksforgeeks.org/how-to-put-x-axis-in-order-month-in-r/ for code
number_of_cases_year_month$month <- factor(number_of_cases_year_month$month, levels = c('Jan', 'Feb', 'Mar', 'Apr', 'May', 'Jun', 'Jul', 'Aug', 'Sep', 'Oct', 'Nov', 'Dec'))

# Referenced: https://stackoverflow.com/questions/12998372/heatmap-like-plot-but-for-categorical-variables to help create heatmap
number_of_cases_year_month |>
  ggplot(mapping = aes(x = month, y = year)) +
  geom_tile(aes(fill = num_of_cases_month_year)) + 
  # Creates two graphs based on the status of the case
  facet_wrap(facets = vars(arrest_was_not_made), dir = "v") +
  scale_fill_gradient(low = "#c2c5aa", high = "#7f4f24", name = "Number of homicides") +
  theme_minimal() +
  labs(x = "Month", y = "Year") 
  # theme(legend.position = "bottom")
```

@@

number_of_cases_city |>
  ggplot(mapping = aes(x = arrest_was_not_made, y = proportion_of_cases)) +
  # Creates two graphs based on the status of the case
  facet_wrap(facets = vars(city), dir = "v") +
  geom_bar(stat = "identity", fill = "#936639") +
  theme_minimal() +
  labs(x = "Status of the homicide case", y = "Proportion of cases") +
  theme(legend.position = "bottom")
```

```{r}
#| label: tbl-city-table
#| tbl-cap: "Proportion and number of solved and unsolved homicides in Los Angeles and New York (2010 to 2017)"
#| echo: false
#| warning: false
#| message: false

@@

number_of_cases_victim_sex |>
  ggplot(mapping = aes(x = victim_sex, y = proportion_of_cases)) +
  # Creates two graphs based on the status of the case
  facet_wrap(facets = vars(arrest_was_not_made)) +
  geom_bar(stat = "identity", fill = "#a4ac86") +
  theme_minimal() +
  labs(x = "Victim's Sex", y = "Proportion of cases") +
  theme(legend.position = "bottom")
```

@@

number_of_cases_victim_race |>
  ggplot(mapping = aes(x = victim_race, y = num_of_cases_victim_race)) +
  # Creates two graphs based on the status of the case
  facet_wrap(facets = vars(arrest_was_not_made)) +
  geom_bar(stat = "identity", fill = "#a4ac86") +
  theme_minimal() +
  labs(x = "Victim's Race", y = "Number of cases") +
  theme(legend.position = "bottom")
```
